---
title: "CHL8010: Statistical Programming and Computation in Health Data"
author: "Week 4 In-class Assignment"
date: "2024-09-30"
format: pdf
embed-resources: true # Produces a standalone HTML file with no external dependencie
---

```{r}
##| label: load-packages
##| include: false
#source("../.Rprofile")
library(here)
library(dplyr)
library(ggplot2)
```


## Perfect your GitHub repo

Some of you may still need to organize your GitHub repo. Use this time to do that. When you are confident with your repo, let me know -- I will try to reproduce your code. 

Your final data should have the following variables (you might have slightly different variable names).
```{r}
finaldata <- read.csv(here("data", "finaldata.csv"), header = TRUE)
names(finaldata)
```


Observations from Canada should look like this...
```{r}
finaldata %>%
  dplyr::filter(country_name == "Canada")
```
Observations from Ecuador should look like this...
```{r}
finaldata %>%
  dplyr::filter(country_name == "Ecuador")
```

## Exploratory data analysis

Use the rest of the class time to explore the final data that will be used for analysis starting next week. At the end of the class, write a summary of your findings and push your **Quarto document (pdf)** to your repo. 

Checking global view of missing data:
```{r}
library(naniar)
finaldata %>% vis_miss()
```

Check trend of a country with known conflicts:
```{r}
finaldata %>% 
  filter(Country.Name == "Afghanistan") %>%
  ggplot(aes(x = Year, y = MaternalMortality)) +
  geom_line() +
  ggtitle("Trend in Maternal Mortality in Afghanistan")
```








